Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-28 paper.qmd
Updated Figure 9 (c)

  ## Compute error
  error_df <- glance(
    df_bin_centroids = df_bin_centroids_scurve_high_dens,
    df_bin = df_bin_scurve_high_dens,
    training_data = training_data_scurve,
    newdata = NULL,
    type_NLDR = "UMAP",
    col_start = "x") |>
    mutate(benchmark_rm_lwd = benchmark_rm_lwd,
           bin1 = effective_bin1_scurve,
           bin2 = effective_bin2_scurve,
           b = bin1 * bin2,
           b_non_empty = NROW(df_bin_centroids_scurve_high_dens),
           mean_counts = sum(df_bin_centroids_scurve_high_dens$bin_counts)/NROW(df_bin_centroids_scurve_high_dens))

@@

mse_scurve_lwd <- ggplot(error_rm_scurve, 
                     aes(x = mean_counts, 
                         y = MSE)) + 
  geom_point(
    size = 1
    ) +
  geom_line(
    linewidth = 0.3
    ) + 
  # geom_vline(xintercept = benchmark1, linetype="solid", 
  #            color = "#bdbdbd", linewidth=1, alpha = 0.5) +
  # scale_x_continuous("standardized bin count", 
  #        transform = "reverse") + 
  scale_x_continuous(breaks = unique(error_rm_scurve$mean_counts)) +
  xlab(expression(mean(n[h]))) +
  ylab("MSE") +
  ggtitle("(c)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

>>>>

  ## Compute error
  error_df <- glance(
    df_bin_centroids = df_bin_centroids_scurve_high_dens,
    df_bin = df_bin_scurve_high_dens,
    training_data = training_data_scurve,
    newdata = NULL,
    type_NLDR = "UMAP",
    col_start = "x") |>
    mutate(benchmark_rm_lwd = round(benchmark_rm_lwd, 2),
           bin1 = effective_bin1_scurve,
           bin2 = effective_bin2_scurve,
           b = bin1 * bin2,
           b_non_empty = NROW(df_bin_centroids_scurve_high_dens),
           mean_counts = sum(df_bin_centroids_scurve_high_dens$bin_counts)/NROW(df_bin_centroids_scurve_high_dens))

@@

mse_scurve_lwd <- ggplot(error_rm_scurve, 
                     aes(x = benchmark_rm_lwd, 
                         y = MSE)) + 
  geom_point(
    size = 1
    ) +
  geom_line(
    linewidth = 0.3
    ) + 
  # geom_vline(xintercept = benchmark1, linetype="solid", 
  #            color = "#bdbdbd", linewidth=1, alpha = 0.5) +
  # scale_x_continuous("standardized bin count", 
  #        transform = "reverse") + 
  scale_x_continuous(breaks = unique(error_rm_scurve$benchmark_rm_lwd)) +
  xlab("threshold to remove low-density hexagons") +
  ylab("MSE") +
  ggtitle("(c)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())
